Title

### 2013-03-31 TCAD2013/overclocking_tcad.tex
modified v1

%% bare_jrnl.tex
%% V1.4
%% 2012/12/27
%% by Michael Shell

\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
%\usepackage{graphicx}
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{../Figures/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  \DeclareGraphicsExtensions{.eps}
\fi
\usepackage{epstopdf}
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

\usepackage{multirow}
\usepackage{amssymb}

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
\usepackage[tight,footnotesize]{subfigure}
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Do not use the stfloats baselinefloat ability as IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

\hyphenation{op-tical net-works semi-conduc-tor}

@@

\title{Title}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Kan~Shi,
        David~Boland,~\IEEEmembership{Member,~IEEE,}
        and~George~A.~Constantinides,~\IEEEmembership{Senior~Memberellow,~IEEE}% <-this % stops a space
	\thanks{K. Shi, D. Boland and G. A. Constantinides are with the Department of Electrical and Electronic Engineering, Imperial College London, London, UK}%
	%\thanks{M. Shell is with the Department of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised December 27, 2012.}}

@@

% make the title area
\maketitle

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}

@@

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

@@

\section{Carry Select Adder}
\subsection{Introduction}

\subsection{Timing Models for $n$-bit Carry Select Adder}
In this section, we describe the modelling method for the CSA timing, with the aim of forming the relationship between the operating frequency and the corresponding maximum word-length of CSA. This information can be employed to determine the truncation error based on the models presented in Section.xxx.

In an $n$-stage CSA, let the stage delay be denoted as $d_{0}\dots d_{n-1}$, where $d_{0}$ and $d_{n-1}$ represent the delay of MSB stage and LSB stage, respectively. In our analysis, we follow the previous assumption that delay is caused due to carry propagation and, in this case, multiplexing. Thus the delay of the $i^{th}$ stage can be obtained through~(\ref{CSA_SingleStageDelay}), where $\mu_{carry}$ denotes the delay of $1$-bit carry propagation and $\mu_{mux}$ denotes the delay of multiplexer.
\begin{eqnarray}\label{CSA_SingleStageDelay}
  d_i=n_i\cdot \mu_{c}+(i+1)\cdot\mu_{mux} 
 % d_0=n_0\cdot \mu_{carry}+\mu_{mux}
\end{eqnarray}

Under the timing-driven design environment, the delay of each stage of CSA is set to be approximately uniform to lead to the fastest operation. In this case we obtain~(\ref{CSA_DelayEqual}).
\begin{eqnarray}\label{CSA_DelayEqual}
  d_0=d_1=\cdots=d_{n-1}
\end{eqnarray}

@@

Therefore the word-length of CSA is given by (\ref{CSA_WL}).
\begin{eqnarray}\label{CSA_WL}
  n_{CSA}=\sum_{i=0}^{n-1}n_{i}=cn_{0}-\frac{\mu_{mux}}{\mu_{carry}}\cdot\frac{(c+1)(c-2)}{2}
\end{eqnarray}

In the conventional situation, the word-length of both RCA and CSA should be truncated in order to meet timing. Hence we obtain~(\ref{CSA_RCA}), where $n_{RCA}$ is determined through (xxx).
\begin{eqnarray}\label{CSA_RCA}
  \mu_{c}\cdot n_{RCA}=\mu_{c}n_0+\mu_{mux}
\end{eqnarray}

Based on~(\ref{CSA_WL}) and~(\ref{CSA_RCA}) we form the relationship between the word-length of CSA and RCA under a given timing constraint, as presented in~(\ref{CSA_Timing}).
\begin{eqnarray}\label{CSA_Timing}
  n_{CSA}=c\cdot n_{RCA}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(c+2)(c-1)}{2}
\end{eqnarray}

%In addition, the word-length of the least significant stage should be greater than 0. Therefore
It can be seen that $c=1$ leads to $n_{CSA}=n_{RCA}$. This is because the least significant stage of CSA is built by RCA. In addition, combining (\ref{CSA_DelayRep}) and (\ref{CSA_RCA}) to ensure that $n_{c-1}>0$. Therefore the stage number is bounded by (\ref{CSA_StageNumber}).
\begin{eqnarray}\label{CSA_StageNumber}
  c<n_{RCA}\cdot\frac{\mu_c}{\mu_{mux}}+1
\end{eqnarray}
%the word-length of each CSA stage is allocated to ensure that

\subsection{Model Verification}
As seen in (\ref{CSA_Timing}), the value of $\mu_{mux}/\mu_c$ should be determined before applying the timing model. This is achieved by keeping $i=0$ in (\ref{CSA_SingleStageDelay}) while varying the value of $n_0$. The corresponding $d_0$ is recorded through the timing analysis tool. Hence $\mu_{mux}/\mu_c$ can be obtained by fitting those values, as presented in Fig.~(\ref{DelayFitting}). Out experimental results show that $\mu_{mux}/\mu_c\approx8$.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3.3in]{./Figures/Fitting.eps}
  \caption{Fitted curve of (\ref{CSA_SingleStageDelay}) for the most significant stage ($i=0$), based on the delay value obtained through the Xilinx Timing Analyzer.}
  \label{DelayFitting}
\end{figure}

Using this information, we verify our model with the results obtained through post place and route simulations of Xilinx Virtex-6 FPGA. Fig.~\ref{CSA Model Verification} demonstrates both the modelled value and the experimental results of the maximum word-length of RCA and 2-stage CSA, respectively, under a given operating frequency. Note that the maximum input word-length is 16-bit, hence the modelled value is set to 16 if it expires. 
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3in]{./Figures/Model.eps}
  \caption{Model Verification.}
  \label{CSA Model Verification}
\end{figure}

% Figure goes here!
It can be seen that our model provide slight conservative outcomes than the experimental data, especially at higher operating frequency. This is because the model coefficients are obtained based on timing analysis, which is designed to ensure correct functionality across a range of operating conditions. In addition, routing delay might be introduced to enlarge the overall delay, while our models consider logic delay only.

\subsection{Area Overhead}
Fig.~\ref{CSA3stage Timing} demonstrates the maximum word-length for RCA and CSA with 2 stages and 3 stages respectively under a range of operating frequencies. We only investigate 3 stages since the maximum stages number predicted in (\ref{CSA_StageNumber}) is 3. It can be seen that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased. This means smaller truncation error can be obtained by CSA for a given frequency. RCA outperforms than CSA when very high frequency is applied, which in turn leads to small word-length for both structures. In addition, the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain, as expected.  
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3.3in]{./Figures/CSA3stage_Timing.eps}
  \caption{Maximum word-length for RCA and CSA across a variety of frequencies.}
  \label{CSA3stage Timing}
\end{figure}
%CSA achieves greater word-length than RCA when frequency is initially increased

However, the accuracy benefits brought by CSA comes with the cost of large area overhead. Fig.~\ref{CSA3stage Area} depicts the resource usage (in terms of the number of Look-Up Tables (LUTs)) used for all three structures. It can be seen that the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the number of the 2-stage CSA is $1.7\times\sim3.1\times$. 
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3.3in]{./Figures/CSA3stage_Area.eps}
  \caption{Area overhead for RCA and CSA.}
  \label{CSA3stage Area}
\end{figure}
%the 3-stage CSA costs

\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
Although advanced architectures such as CSA inheritly offer better performance than the basic structure, this would generate a large area overhead. In the following experiments, the trade-offs between accuracy, performance as well as area are explored. If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented. This potentially generate truncation errors. For instance, the number of available LUTs is set to 45, 35, 25 and 15 respectively, while timing requirements are met by reducing the input word-length of each architecture. In addition, we also investigate the scenario where RCA is implemented with the maximum possible word-length under the given area constraint, while meeting timing by overclocking. The corresponding error expectations of these scenarios are depicted in Fig.xxx. The optimal design method which achieves the minimum error expectation is labelled.
\begin{figure}[htbp]
	\centering
	\includegraphics[width=3.3in]{./Figures/Error_LUT45.eps}
	\caption{LUT=45}
\end{figure}

@@

If there is no area limitation, CSA with higher stage numbers will be the optimal design choice unless very high frequencies are applied. This is because a long carry chain is divided into multiple overlapped sections in comparison to RCA, and the higher stage number the shorter the carry chain length of each stage. When the frequency increases, however, the multiplexer delay becomes comparable to the carry chain delay, and this will limit the maximum word-length of CSA. It can be seen that the overclocked RCA outperforms at higher frequencies.

For a tighter area budget, only part of the complex structures can be implemented, while the simple structure still keep full precision. As can be seen in Fig.xxx and Fig.xxx, area instead of timing becomes dominate when the frequency is initially increased. This lead to the truncation of word-length of both 2-stage and 3-stage CSA. For an even stringent area constraint, the word-length of RCA is limited, meanwhile CSA with high stage numbers could not be implemented, as shown in Fig.xxx. In this situation the overclocked RCA achieves best accuracy across the whole frequency domain.

In general, the error expectations at the output of all four design method for a variety of timing and area constraints are demonstrated in Fig.~\ref{Tradeoff}.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3.3in]{./Figures/Tradeoff.eps}
  \caption{Trade-offs between accuracy, performance and area for 4 design methodologies.}
  \label{Tradeoff}
\end{figure}

>>>>

%% overclocking_tcad.tex
%% by Kan Shi

%\usepackage{times,epsfig,amsfonts,bm}
%\usepackage{pdflscape}
%\usepackage{afterpage}
%\usepackage{algorithm}
%\usepackage{algorithmic}
%\usepackage{fmtcount,threeparttable, setspace, nicefrac}
%\usepackage[dvips]{color}
%\usepackage{amsthm}

\documentclass[journal]{IEEEtran}
\usepackage{cite}

\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{../Figures/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  \DeclareGraphicsExtensions{.eps}
\fi
\usepackage{epstopdf}

\usepackage{multirow}
\usepackage{amssymb}
\usepackage[cmex10]{amsmath}
%\usepackage{algorithmic}
%\usepackage{array}
\usepackage[tight,footnotesize]{subfigure}
\usepackage{stfloats}

@@

\title{Title}

\author{Kan~Shi,
        David~Boland,~\IEEEmembership{Member,~IEEE,}
        and~George~A.~Constantinides,~\IEEEmembership{Senior~Member,~IEEE}% <-this % stops a space
	\thanks{K. Shi, D. Boland and G. A. Constantinides are with the Department of Electrical and Electronic Engineering, Imperial College London, London, SW7 2BT, U.K. (email: {}@imperial.ac.uk)}%
	%\thanks{M. Shell is with the Department of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised December 27, 2012.}}

@@

\maketitle

@@

\begin{IEEEkeywords}

@@

@@

\section{Carry Select Adder}
\subsection{Introduction}
Since the delay of RCA is determined by the length of carry chain, there are several alternative adder architectures proposed to shorten the carry chain. For instance, the carry select adder (CSA) is designed to overlap carry propagation in sections such that the operating speed can be boosted. In a CSA, the carry chain is divided into multiple stages. Each stage contains two RCAs and two multiplexers. For a given input, computations are performed twice simultaneously, with the carry input as zero and one respectively. The results are then selected according to the actual carry input. Although this structure brings timing benefits, it costs extra hardware resources than RCA as the carry chain is duplicated and multiplexers are expensive especially in the FPGA technology. In this section, silicon area is incorporated as the third metric besides accuracy and performance. We explore the trade-offs between these three factors for both adder structures. The objective is to demonstrate the best design choice for a given set of design constraints.

%In addition to RCA, there are several

\subsection{Timing Models for $n$-bit Carry Select Adder}
We initially describe the modelling method for the CSA timing, with the aim of forming the relationship between the operating frequency and the corresponding maximum word-length of CSA. This information can be employed to determine the truncation error based on the models presented in Section.xxx.

In a CSA with $c$ stages, let the stage delay be denoted by $d_{0}\dots d_{c-1}$, where $d_{0}$ and $d_{c-1}$ represent the delay of the most significant stage and the least significant stage, respectively. Unlike other stages, the least significant stage is built by one RCA only, since it is directly driven by the carry input. In our analysis, we follow the previous assumption that delay is due to carry propagation as well as, in this case, multiplexing the carry output. Therefore the delay of the $i^{th}$ stage can be obtained through~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$ denotes the delay of $1$-bit carry propagation and $\mu_{mux}$ denotes the delay of multiplexing.
\begin{eqnarray}\label{CSA_SingleStageDelay}
  d_i=n_i\cdot \mu_{c}+(i+1)\cdot\mu_{mux} 
 % d_0=n_0\cdot \mu_{carry}+\mu_{mux}
\end{eqnarray}

Under the timing-driven design environment, the delay of each stage of CSA is set to be approximately uniform for the fastest operation. In this case we obtain~(\ref{CSA_DelayEqual}).
\begin{eqnarray}\label{CSA_DelayEqual}
  d_0=d_1=\cdots=d_{n-1}
\end{eqnarray}

@@

The word-length of CSA is then given by (\ref{CSA_WL}).
\begin{eqnarray}\label{CSA_WL}
  n_{CSA}=\sum_{i=0}^{n-1}n_{i}=cn_{0}-\frac{\mu_{mux}}{\mu_{carry}}\cdot\frac{(c+1)(c-2)}{2}
\end{eqnarray}

In the conventional situation, the word-length of both RCA and CSA should be properly selected in order to meet timing. In this case,~(\ref{CSA_RCA}) can be obtained, where $n_{RCA}$ is determined by current timing information through (xxx).
\begin{eqnarray}\label{CSA_RCA}
  \mu_{c}\cdot n_{RCA}=\mu_{c}n_0+\mu_{mux}
\end{eqnarray}

Based on~(\ref{CSA_WL}) and~(\ref{CSA_RCA}), we may obtain the representation of the word-length of CSA in terms of a given timing constraint, as presented in~(\ref{CSA_Timing}).
% we form the relationship between the word-length of CSA and RCA under a given timing constraint, as presented in~(\ref{CSA_Timing}).
\begin{eqnarray}\label{CSA_Timing}
  n_{CSA}=c\cdot n_{RCA}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(c+2)(c-1)}{2}
\end{eqnarray}

It can be seen that $c=1$ leads to $n_{CSA}=n_{RCA}$. This is because RCA forms the least significant stage of CSA. In addition, combine (\ref{CSA_DelayRep}) and (\ref{CSA_RCA}) to ensure $n_{c-1}>0$, we obtain the upper bond of the stage number by~(\ref{CSA_StageNumber}).
\begin{eqnarray}\label{CSA_StageNumber}
  c<n_{RCA}\cdot\frac{\mu_c}{\mu_{mux}}+1
\end{eqnarray}
%the word-length of each CSA stage is allocated to ensure that

\subsection{Model Verification}
As seen in (\ref{CSA_Timing}), the value of $\mu_{mux}/\mu_c$ should be determined before applying the timing model. This ratio can be obtained through timing analysis. Specifically, varying the word-length of a single stage $n_i$ and recording the corresponding delay value $d_i$ through the timing analysis tool. According to~(\ref{CSA_SingleStageDelay}), the ratio can be obtained by fitting those values using linear polynomials, as presented in Fig.~(\ref{DelayFitting}). Out experimental results show that $\mu_{mux}/\mu_c\approx8$.
%keeping $i=0$ in (\ref{CSA_SingleStageDelay}) while varying the value of $n_0$. The corresponding delay value $d_0$ is recorded through the timing analysis tool. Hence $\mu_{mux}/\mu_c$ can be obtained by fitting those values, as presented in Fig.~(\ref{DelayFitting}). Out experimental results show that $\mu_{mux}/\mu_c\approx8$.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3.3in]{./Figures/Fitting.eps}
  \caption{Fitted curve of (\ref{CSA_SingleStageDelay}) for the most significant stage ($i=0$), based on the given input word-length and the corresponding delay value obtained through the Xilinx Timing Analyzer.}
  \label{DelayFitting}
\end{figure}

Using this information, we verify our timing model with experimental results, which are obtained from post place and route simulations on Xilinx Virtex-6 FPGAs. Fig.~\ref{CSA Model Verification} demonstrates both the modelled value and the experimental results of the maximum word-length of RCA and 2-stage CSA, respectively, across a range of operating frequencies. The maximum input word-length in our experiments is 16-bit, hence the modelled value is set to 16 if it expires. 
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3in]{./Figures/Model.eps}
  \caption{Comparison of the maximum word-length for a given operating frequency between the modelled value and the experimental results from FPGA simulations.}
  \label{CSA Model Verification}
\end{figure}

% Figure goes here!
It can be seen that our timing models match well the experimental results for both RCA and CSA, except that the modelled outcomes are slight conservative, especially at higher operating frequencies. This is because the model coefficients are obtained based on timing analysis, which is designed with safety margins to ensure correct functionality for diverse operating conditions. In addition, routing delay might be introduced during timing analysis such that the overall delay is enlarged, while our models consider logic delay only.

% provide slight conservative outcomes than the experimental data, especially at higher operating frequencies. 
.

\subsection{Area Overhead}
Fig.~\ref{CSA3stage Timing} demonstrates the maximum word-lengths for RCA and CSA with 2 stages and 3 stages under a range of operating frequencies. We only investigate 3 stages as the maximum stages number predicted in (\ref{CSA_StageNumber}) is 3. It can be seen that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased. This corresponds to smaller truncation errors. RCA only outperforms than CSA when very high frequency is applied. In addition, the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain, as expected.  
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3.3in]{./Figures/CSA3stage_Timing.eps}
  \caption{Maximum word-length for RCA and CSA across a variety of frequencies.}
  \label{CSA3stage Timing}
\end{figure}
%CSA achieves greater word-length than RCA when frequency is initially increased

However, the accuracy benefits brought by CSA comes with the cost of large area overhead. Fig.~\ref{CSA3stage Area} depicts the resource usage (in terms of the number of Look-Up Tables (LUTs) in the FPGA) used for all three structures. It can be seen that for a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the number of the 2-stage CSA is $1.7\times\sim3.1\times$. This finding poses a question of whether CSA with higher stage numbers still offer better accuracy than RCA under a limited area budget.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3.3in]{./Figures/CSA3stage_Area.eps}
  \caption{Area overhead for RCA and CSA.}
  \label{CSA3stage Area}
\end{figure}
%the 3-stage CSA costs

\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
%Although advanced architectures such as CSA inheritly offer better performance than the basic structure, this would generate a large area overhead. In the following experiments, 
To answer this question, we explore the trade-offs between accuracy, performance as well as area in this section. If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented. The precision lose might generates large errors even at low frequencies. This is demonstrated by experiments where an area constraint is applied besides the timing requirement. Both of the constraints are met by reducing the word-length of the input signal. The errors at the outputs are recorded with the reference to the original word-length. In addition, another designing method is adopted where RCA is implemented with the maximum possible word-length under the given area budget, while the timing constraints are met by overclocking. For instance, Fig.xxx to Fig.xxx illustrate error expectations of all the described design scenarios when setting the LUTs number to 45, 35, 25 and 15 respectively. The optimal design metric with the minimum error expectation is labelled for each area constraint.
%
% the number of available LUTs is set to 45, 35, 25 and 15 respectively, while timing requirements are met by reducing the input word-length of each architecture. In addition, we also investigate the scenario where RCA is implemented with the maximum possible word-length under the given area constraint, while meeting timing by overclocking. The corresponding error expectations of these scenarios are depicted in Fig.xxx. The optimal design method which achieves the minimum error expectation is labelled.
\begin{figure}[htbp]
	\centering
	\includegraphics[width=3.3in]{./Figures/Error_LUT45.eps}
	\caption{LUT=45}
\end{figure}

@@

If the available area is large enough, as shown in Fig.xxx, CSA with higher stage numbers can be implemented with full precision and it is the optimal design choice unless very high frequencies are applied. This is because at lower frequencies, the long carry chain is divided into multiple overlapped sections, and the higher stage number the shorter the carry chain length of each stage. When the frequency increases, however, the multiplexer delay becomes comparable to the carry chain delay, and this will limit the maximum word-length of CSA. It can be seen that the overclocked RCA achieves best accuracy at higher frequencies.

For a tighter area budget, only part of the complex structures can be implemented, whilst the simple structure still keeps full precision. As can be seen in Fig.xxx and Fig.xxx, area instead of timing becomes the dominate factor when frequency is initially increased. This lead to a large truncation error for both 2-stage and 3-stage CSA. In this situation, overclocking RCA serves as the optimum choice with respect to accuracy.

For an even stringent area constraint, the word-length of RCA is also limited. This results in truncation error initially for all design scenarios, as shown in Fig.xxx. Meanwhile, CSA with high stage numbers could not be implemented at all. In this situation the overclocked RCA achieves best accuracy across the whole frequency domain.

In general, the error expectations at the output of all four design method for a set of timing and area constraints are demonstrated in Fig.~\ref{Tradeoff}.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3.3in]{./Figures/Tradeoff.eps}
  \caption{Trade-offs between accuracy, performance and area for 4 design methodologies.}
  \label{Tradeoff}
\end{figure}
